### 2017-07-14 README.Rmd
update implementation status

One categorical (>2 level) - GoF  (not yet implemented)

```
mtcars %>%
  specify(response = cyl) %>% # alt: cyl ~ 1
  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "chisq")
```

Two categorical (>2 level) variables  (not yet implemented)

```
mtcars %>%
  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

>>>>

One categorical (>2 level) - GoF  (implemented)

```
mtcars %>%
  specify(cyl ~ NULL) %>% # alt: response = cyl
  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "Chisq")
```

Two categorical (>2 level) variables  (implemented)

```
mtcars %>%
  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "Chisq")
```

One numerical variable one categorical (2 levels) (diff in means) (implemented)
